Manuscript

### 2022-09-01 analysis/manuscript.Rmd
fix small typo

write.table(corr_potential_trait_confounders_pos_MVMR_summary, "output/tables/C_summ_MVMR_result.csv")
# 
# corr_potential_trait_confounders_pos_MVMR_summary <- corr_potential_trait_confounders_pos_MVMR_summary %>% 
#   group_by(outcome_ID) %>%
#   mutate(corr_due_to_confounding_MVMR_summ = sum(corr_due_to_confounding_MVMR)) %>%
#   mutate(corr_due_to_confounding_summ = sum(corr_due_to_confounding))

@@

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = same_trait_corr_minus_MR_est - 1.96*corr_due_to_confounding_summ_SE, 
                 ymax = same_trait_corr_minus_MR_est + 1.96*corr_due_to_confounding_summ_SE),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = corr_due_to_confounding_summ - 1.96*Z_prod_se, 
                 xmax = corr_due_to_confounding_summ + 1.96*Z_prod_se),
    colour = "grey",
    width = 0
  ) +

>>>>

write.table(corr_potential_trait_confounders_pos_MVMR_summary, "output/tables/C_summ_MVMR_result.csv")

corr_potential_trait_confounders_pos_MVMR_summary <- corr_potential_trait_confounders_pos_MVMR_summary %>% 
  group_by(outcome_ID) %>%
  mutate(corr_due_to_confounding_MVMR_summ = sum(corr_due_to_confounding_MVMR)) %>%
  mutate(corr_due_to_confounding_summ = sum(corr_due_to_confounding))

@@

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = same_trait_corr_minus_MR_est - 1.96*same_trait_corr_minus_MR_est_se, 
                 ymax = same_trait_corr_minus_MR_est + 1.96*same_trait_corr_minus_MR_est_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = corr_due_to_confounding_summ - 1.96*corr_due_to_confounding_summ_SE, 
                 xmax = corr_due_to_confounding_summ + 1.96*corr_due_to_confounding_summ_SE),
    colour = "grey",
    width = 0
  ) +
